---
title: "STAT_5361_Hw9"
author: "Yicheng Guo"
date: "2020/11/11"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Ex 7.5.1

## (1)

Pdf of x is

$$
f(x) = \frac{1}{5\sqrt{2\pi}}x^2 e^{-\frac{(x-2)^2}{2}}, \qquad -\infty <x < \infty.
$$

So  

$$
E(x^2) = \int_{-\infty}^\infty x^2 f(x) dx
$$

Now g(x) is standard normal,

$$
E(x_i^2) \approx \frac1n \sum\frac{x_i^4e^{-\frac{(x_i-2)^2}{2}}}{5e^{-\frac{x_i^2}{2}}} = \frac1{5n} \sum x_i^4e^{2x_i-2}, x_i \sim N(0,1)
$$
```{r}

g1 <- function(x) x^4 * exp(2*x - 2)
m1 <- function(x) x^3 * exp(2*x - 2)
set.seed(7511)
Sample751a1 <- rnorm(1000)
Sample751a2 <- rnorm(10000)
Sample751a3 <- rnorm(50000)

est751a1 <- g1(Sample751a1)
est751a2 <- g1(Sample751a2)
est751a3 <- g1(Sample751a3)
xsqresult751a <- list(mean(est751a1)/5, mean(est751a2)/5, mean(est751a3)/5)
names(xsqresult751a) <- c("XSQEst._1000", "XSQEst._10000", "XSQEst._50000") 
est751a1e <- m1(Sample751a1)
est751a2e <- m1(Sample751a2)
est751a3e <- m1(Sample751a3)
xresult751a <- list(xsqresult751a$XSQEst._1000 - (mean(est751a1e) /5)^2,
                   xsqresult751a$XSQEst._10000 - (mean(est751a2e) /5)^2,
                   xsqresult751a$XSQEst._50000 - (mean(est751a3e) /5)^2)
names(xresult751a) <- c("VarEst._1000", "VarEst._10000", "VarEst._50000") 
xsqresult751a
xresult751a
```


## (2)

Take g2(x) to be N(2, 1),

$$
E(x_i^2) \approx \frac1{5n} \sum x_i^4, x_i \sim N(2,1)
$$

Compared with other possible methods, this one is most efficient in calculation, since the sampling is easy, and in estimation we only need to multiply.

## (3)

```{r}
g2 <- function(x) x^4
set.seed(7512)
Sample751b1 <- rnorm(1000, 2)
Sample751b2 <- rnorm(10000, 2)
Sample751b3 <- rnorm(50000, 2)
est751b1 <- g2(Sample751b1)
est751b2 <- g2(Sample751b2)
est751b3 <- g2(Sample751b3)
xsqresult751b <- list(mean(est751b1)/5, mean(est751b2)/5, mean(est751b3)/5)
names(xsqresult751b) <- c("XSQEst._1000", "XSQEst._10000", "XSQEst._50000") 
xsqresult751b
```

## (4)
```{r}
microbenchmark::microbenchmark(g1(Sample751a1), g2(Sample751b1), times = 10000L)
```

From result in microbenchmark, we can see that the efficiency of the second method is approximately twice faster than the first one.

# Ex 7.5.2

## (1)
```{r}
s0 <- 1; r <- 0.05; n <- 12
S <- function(t, rate, sigma, s0) s0 * exp((rate - 0.5 * sigma^2) * t + sigma * sqrt(t) * rnorm(1))
S_PATH <- function(n, t, rate, sigma, s0){
  Path <- vector(length = n)
  Path[1] <- S(t/n, rate, sigma, s0)
  for (i in 2:n) {
    temp <- Path[i-1]
    Path[i] <- S(t/n, rate, sigma, temp)
  }
  return(Path)
}
```

## (2)

Write simulation function and correlation-summary function.
```{r}
SingleSIMU <- function(n, t, rate, sigma, s0, K){
  PATH <- S_PATH(n, t, rate, sigma, s0)
  SA <- mean(PATH); SG <- prod(S_PATH(n, t, rate, sigma, s0))^(1/n)
  v <- exp(-1 * rate * t)
  PA_Num <- v * max(SA - K, 0)
  PG_Num <- v * max(SG - K, 0) 
  PE_Num <- v * max(PATH[n] - K, 0)
  result <- list(PA_Num, PG_Num, PE_Num, PATH[n])
  names(result) <- c("PAVal", "PGVal", "PEVal", "S_T")
  return(result)
}
MultiSIMU <- function(sample_size, n, t, rate, sigma, s0, K){
  result <- SingleSIMU(n, t, rate, sigma, s0, K)
  for(i in 1:sample_size){
    temp <- SingleSIMU(n, t, rate, sigma, s0, K)
    result$PAVal <- append(result$PAVal, temp$PAVal)
    result$PGVal <- append(result$PGVal, temp$PGVal)
    result$PEVal <- append(result$PEVal, temp$PEVal)
    result$S_T <- append(result$S_T, temp$S_T)
  }
  return(result)
}
SummaryofP2cor <- function(P){
  L1 <- cor(P$PAVal, P$PGVal); L2 <- cor(P$PAVal, P$PEVal)
  L3 <- cor(P$PAVal, P$S_T)
  result <- list(L1, L2, L3)
  names(result) <- c('cor_with_PGVal', 'cor_with_PEVal', 'cor_with_ST')
  return(result)
}
```

Initial value for (2) and simulate:
```{r}
K2 <- seq(1.1, 1.5, 0.1); sigma2 <- 0.5; T2 <- 1
set.seed(7521)
P2Q2K1.1 <- MultiSIMU(5000, n, T2, r, sigma2, s0, K2[1])
P2Q2K1.2 <- MultiSIMU(5000, n, T2, r, sigma2, s0, K2[2])
P2Q2K1.3 <- MultiSIMU(5000, n, T2, r, sigma2, s0, K2[3])
P2Q2K1.4 <- MultiSIMU(5000, n, T2, r, sigma2, s0, K2[4])
P2Q2K1.5 <- MultiSIMU(5000, n, T2, r, sigma2, s0, K2[5])
SummaryofP2cor(P2Q2K1.1)
SummaryofP2cor(P2Q2K1.2)
SummaryofP2cor(P2Q2K1.3)
SummaryofP2cor(P2Q2K1.4)
SummaryofP2cor(P2Q2K1.5)
```

From the result, we can see that as K increase, $P_A$'s correlation coefficient with $S(T)$ and $P_E$ are decreasing(not that apparent for $P_E$ in my trial sampling process), and with $P_G$ is always approximately 0.

## (3)
In (3) and (4), codes are similar to that of (2) except initial value.
```{r}
  #Q3
K3 <- 1.5; sigma3 <- seq(0.2, 0.5, 0.1); T3 <- 1
set.seed(7523)
P2Q3s0.2 <- MultiSIMU(5000, n, T3, r, sigma3[1], s0, K3)
P2Q3s0.3 <- MultiSIMU(5000, n, T3, r, sigma3[2], s0, K3)
P2Q3s0.4 <- MultiSIMU(5000, n, T3, r, sigma3[3], s0, K3)
P2Q3s0.5 <- MultiSIMU(5000, n, T3, r, sigma3[4], s0, K3)
SummaryofP2cor(P2Q3s0.2)
SummaryofP2cor(P2Q3s0.3)
SummaryofP2cor(P2Q3s0.4)
SummaryofP2cor(P2Q3s0.5)
```

From the results, we can see that as $\sigma$ increase, $P_A$'s correlation coefficient with $S(T)$ and $P_E$ are increasing, and with $P_G$ is always approximately 0.

## (4)
```{r}
K4 <- 1.5; sigma4 <- 0.5; T4 <- seq(0.4, 1.6, 0.3)
set.seed(7524)
P2Q4t0.4 <- MultiSIMU(5000, n, T4[1], r, sigma4, s0, K4)
P2Q4t0.7 <- MultiSIMU(5000, n, T4[2], r, sigma4, s0, K4)
P2Q4t1.0 <- MultiSIMU(5000, n, T4[3], r, sigma4, s0, K4)
P2Q4t1.3 <- MultiSIMU(5000, n, T4[4], r, sigma4, s0, K4)
P2Q4t1.6 <- MultiSIMU(5000, n, T4[5], r, sigma4, s0, K4)
SummaryofP2cor(P2Q4t0.4)
SummaryofP2cor(P2Q4t0.7)
SummaryofP2cor(P2Q4t1.0)
SummaryofP2cor(P2Q4t1.3)
SummaryofP2cor(P2Q4t1.6)
```

we can see that as time increase, $P_A$'s correlation coefficient with $S(T)$ and $P_E$ are increasing, and with $P_G$ is always approximately 0.

## (5)
